Evolution of solar wind discontinuities in the inner heliosphere

### 2024-05-11 article.qmd
update

![](figures/density_distribution){#fig-distribution}

![](figures/thickness_current){#fig-thickness-current}

@@

![Comparision map of (normalized) thickness and (normalized) current density](figures/enc2/thickness_current_spc_n_spc.png){#fig-comp-map}

>>>>

![](figures/density_distribution.png

![](figures/enc2/thickness_current.spc_n_spc.png)

@@

![Comparision map of (normalized) thickness and (normalized) current density](figures/enc2/thickness_current.spc_n_spc.png){#fig-comp-map}
